First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-05-14 ms.tex
Starting to change text to match new(er) figures

The resulting one dimensional power spectra are shown in Figure~\ref{fig:1d_ps}, where 
the measured power is shown with solid blue, the 1-$\sigma$ noise level is shown with 
dashed red, and the 2-$\sigma$ upper limit for each bin is shown with dashed magenta. 
Where our unbiased estimator is negative, the absolute value is shown, but with a dashed 
green line. For consistency with the literature, we plot our one dimensional power spectra 
as $\Delta^2(k)=k^3P_{21}(k)/(2\pi^2)$, which has units of mK$^2$.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{1D_spectra.pdf}
\caption[1D deep power spectra]{
One dimensional power spectra for our three sub-bands and both instrumental 
polarizations. The solid blue line shows the measured power spectrum with step widths 
corresponding to the bin size used in the average. Where the measured signal is negative 
we plot the absolute value in green. The red dashed line is the 1-$\sigma$ noise level, and 
the dashed magenta line is the 2-$\sigma$ upper limit for each $k$ bin. Theoretical models 
from \citet{Lidz:2008} for $\overline{x}_i=0.54$, $0.82$, and $0.96$ are shown in the low, 
mid, and high band spectra, respectively, in solid black. from \citet{Lidz:2008} are shown in 
solid black. An additional theoretical model for a fully neutral IGM from 
\citet{Furlanetto:2006} is shown with a dashed black line.
\label{fig:1d_ps}
}
\end{center}
\end{figure*}

In all bands and polarizations, we are heavily signal dominated in our most sensitive region 
(low $k$). This is not surprising based on the 2D spectra we examined earlier. We can see 
the strong coarse band harmonic lines, and the cable reflection line between the first two 
coarse band lines. But between these coarse lines there are bins which approach the noise 
level and are consistent with zero (notably the North-South polarization for the $z=7.1$ and 
$z=6.8$ bands). These regions are encouraging because they have the potential to 
continue integrating down with more data.

>>>>

The resulting one dimensional power spectra are shown in Figure~\ref{fig:1d_ps}, where 
the measured power is shown with solid blue, the 1-$\sigma$ noise level is shown with 
thin red, and the 2-$\sigma$ upper limit for each bin is shown with dashed magenta. 
Where our unbiased estimator is negative, the absolute value is shown, but with a dotted 
blue line. For consistency with the literature, we plot our one dimensional power spectra 
as $\Delta^2(k)=k^3P_{21}(k)/(2\pi^2)$, which has units of mK$^2$.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{1D_spectra.pdf}
\caption[1D deep power spectra]{
One dimensional power spectra for our three sub-bands and both instrumental 
polarizations. The solid blue line shows the measured power spectrum with step widths 
corresponding to the bin size used in the average. Where the measured signal is negative 
we plot the absolute value with a dotted line. The thin red line is the 1-$\sigma$ noise level, and 
the dashed magenta line is the 2-$\sigma$ upper limit for each $k$ bin. 
A fiducial theoretical model for a fully neutral IGM from \citet{Furlanetto:2006} is shown
in black for reference.
\label{fig:1d_ps}
}
\end{center}
\end{figure*}

\textcolor{red}{this needs to be rewritten}
In all bands and polarizations, we are heavily signal dominated in our most sensitive region 
(low $k$). This is not surprising based on the 2D spectra we examined earlier. We can see 
the strong coarse band harmonic lines, and the cable reflection line between the first two 
coarse band lines. But between these coarse lines there are bins which approach the noise 
level and are consistent with zero (notably the North-South polarization for the $z=7.1$ and 
$z=6.8$ bands). These regions are encouraging because they have the potential to 
continue integrating down with more data.
